Stabilization-Free Virtual Element Methods

### 2023-06-24 ex_shared.tex
revise the paper based on the reports
update funding and reference file

% Sets running headers as well as PDF title and authors
\headers{Stabilization-Free VEM}{C. Chen, X. Huang and H. Wei}

% Title. If the supplement option is on, then "Supplementary Material"
% is automatically inserted before the title.
\title{Stabilization-Free Virtual Element Methods\thanks{\today
\funding{%The second author is the corresponding author. 
The second author was supported by the National Natural Science Foundation of China Project 12171300, and the Natural Science Foundation of Shanghai 21ZR1480500. The first and third authors were supported by NSFC (11871413).}}}

>>>>

% Sets running headers as well as PDF title and authors
\headers{VEM Without Extrinsic Stabilization}{C. Chen, X. Huang and H. Wei}

% Title. If the supplement option is on, then "Supplementary Material"
% is automatically inserted before the title.
\title{Virtual Element Methods Without Extrinsic Stabilization\thanks{\today
\funding{%The second author is the corresponding author. 
The second author was supported by the National Natural Science Foundation of
China {\color{red} (NSFC) (Grant No. 12171300)}, and the Natural Science Foundation of Shanghai
{\color{red}(Grant No. 21ZR1480500)}. The first and third authors were supported by the National Natural
Science Foundation of China (NSFC) (Grant No. 12261131501, 11871413), and the construction of innovative provinces in Hunan Province (Grant No. 2021GK1010)}}}
